 Assignment 1, Manasa Pullabhatla,  811284922
 
 
### Install the ISLR library using the install.packages() command. Call the library using the library(ISLR) command to ensure that the library is correctly installed.
```{r}
# install.packages("ISLR") - Commenting out the package since it's already installed

library("ISLR")
```

 
### Create a new R-Notebook (.Rmd) file. In the first code chunk, call the ISLR library and then print the summary of the Carseats dataset. How many observations (rows) this dataset contains?
```{r}
df <- Carseats

summary(df)
```
### Using the summary statistics shown above, what is maximum value of the advertising attribute? 

```{r}

max(df $Advertising)
```
### Calculate the IQR of the Price attribute

```{r}
IQR(df $Price)
```
### Plot the Sales against Price. What do you see in there? 
 
```{r}
plot(x = df$Sales, y = df$Price, 
     xlab = "sales", ylab = "price", main = "Sales against Price")
```

### Calculate the correlation of the two attributes. What does the sign of the correlation coefficient suggest?
 
```{r}
cor(x = df $Sales, y = df $Price)
```
From the above visual and function it is understood that the correlation between sales and price is -0.4449507, it indicates a  negative coorelation, implying that as prices increase, sales tend to decrease to an extent.
 
 